\documentclass{article}

\title{Team Agreement}
\date{\today}
\author{Team name}

\begin{document}
\pagenumbering{gobble}
    \input{sections/title.tex}
    \newpage
    \pagenumbering{arabic}
    \section{Team name and leader}
    \subsection{Team name} Pos application
    \subsection{Leader} Our leader is \textbf{Rytis Tauras} and the co-leader is Matas Čeplinskas.\\[0,25cm] We decided on it by letting AI analyze our abilities and randomly generating 30 votes on who should take the lead.\\[0,25cm]
    \textbf{Leaders responsibilities:} organizing meetings, managing the main repository, identifying tasks for a given time period, communication with lecturer.\\[0,25cm]
    \textbf{Leader authority:} strong worded letters, mandatory private meetings for rule breaking, ability to designate part of their responsibilities to another team member.
    The reason we chose this method is because we wanted a method between democracy and chance. 
    \section{Team ambition} Desired grade - 9 or higher.
    \section{Decision making approach and key team rules} \textbf{Decision making:} majority vote.\\[0,25cm]
    \textbf{Key team rules:} \begin{itemize}
        \item one veto vote for each team member
        \item no absence without notice
        \item check the team chat at least 2 times per day
        \item respond to direct questions in chat
    \end{itemize} 
    \section{Key principles governing work distribution} Distributing work based on ability, personal constraints and team agreement.
    Communication if there is too much or too little work.
    \section{Capacity constraints} Based on communication on weekly basis.
    \section{Team meeting times and group work} Meetings in person on Thursdays at 2pm or other days based on agreement.\\ Meetings online with lecturer on Fridays 2pm if it's needed.
    \section{Team progress tracking} Stand-ups on weekly meetings and updates on individual progress during the week.
    \section{Sanctions and punishment} Written apology and explanation to other team members.\\[0,25cm]In case of long-term (2 weeks+) absence, unreasonable lack of contribution or bad behavior - escalation to involving the lecturer
    
\end{document}
